\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-01-30 doc/USER_MANUAL/manual_SPECFEM3D.tex
updated the manual to describe the options one may need to change in flags.guess

>>>>

Before running the \texttt{configure} script, you should probably edit file \texttt{flags.guess} to make sure that it contains the best compiler options for your system. Known problems or things to check are:

\begin{description}
\item [{\texttt{Intel ifort compiler}}] See if you need to add \texttt{-assume byterecl} for your machine.
\item [{\texttt{IBM or Cray compilers}}] See if you need to add \texttt{-qsave} or \texttt{-qnosave} for your machine.
\item [{\texttt{Mac OS}}] You will probably need to install \texttt{XCODE}.
In addition, the \texttt{clock\_gettime} routine, which is used by the \texttt{SCOTCH} library that we use, does not exist in Mac OS.
You will need to replace it with \texttt{clock\_get\_time} if you want to use \texttt{SCOTCH}.
\end{description}
